# Basic dataset sizes in AnVIL workspaces visible to AnVIL_Devs

VJ Carey, BJ Stubbs



```{r setup, echo=FALSE, results="hide"}
suppressMessages({
library(AnVIL)
library(rjson)
library(httr)
library(tibble)
library(dplyr)
library(magrittr)
})

participantCount = function(studyTitle) {
 types = httr::content(
  terra$getEntityTypes("anvil-datastorage",
    studyTitle))
 types$participant$count
}

sampleAtts = function(studyTitle) {
 atts = httr::content(
  terra$getEntities(
    "anvil-datastorage",
    studyTitle,
     "sample"))
 atts
}

basicDataFrame = function() {
  ws = AnVIL::terra$listWorkspaces()
  wscon = content(ws, type="text/json") 
  ww = fromJSON(wscon)
  alln = sapply(ww, function(x) x$workspace$name)
  anvnames = grep("AnVIL", alln, value=TRUE) -> anvnames
  toks = strsplit(anvnames, "_")
  stud = sapply(toks, "[", 2)
  site = sapply(toks, "[", 3)
  org = sapply(toks, "[", 4)
  t5 = sapply(toks, "[", 5)
  t6 = sapply(toks, "[", 6)
  nums = lapply(anvnames, participantCount)
  bad = which(sapply(nums, is.null))
  if (length(bad)>0) {
    nums[bad]=NA
    nums = unlist(nums)
    }
  data.frame(study=stud, site=site, organ=org, 
    N=nums, addit=t5, ext=t6, name=anvnames, 
    stringsAsFactors=FALSE)
}

setClass("AnVILStudies",
 representation(basic="data.frame"))
AnVILStudies = function(dataframe) {
 new("AnVILStudies", basic=dataframe) }
setMethod("show", "AnVILStudies", function(object) {
 print(as_tibble(object@basic))
})
#sa = sampleAtts("AnVIL_CCDG_WashU_CVD_EOCAD_Emerge_WGS")

```

```{r getbasic}
basedf = basicDataFrame()
```
We are using the AnVIL package of Bioconductor to
query and summarize the AnVIL workspaces.  There are
`r nrow(basedf)` workspaces with 'AnVIL' as the
leading substring of workspace name.

```{r baic}
as_tibble(basedf)
```

The number of samples is usually available in an
attribute, but there are `r sum(is.na(basedf$N))`
studies where this is not available.

It is of interest to tabulate numbers of samples
by anatomic organ.
```{r byorg}
as_tibble(basedf) %>% 
  group_by(study, organ) %>% 
  summarise(N=sum(N, na.rm=TRUE))
```

For CCDG we can partition a bit more finely.

```{r doccd}
basedf %>% filter(study=="CCDG") %>% 
  group_by(study,organ,addit) %>% 
  summarise(N=sum(N, na.rm=TRUE))
```
